%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{rajan}{maurya}
       {Software developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    C-42/2, Street No-3
    Gamri Extention,
    Fifth Pushta Delhi-110053
    ~
    \href{mailto:rajanmaurya154@gmail.com}{rajanmaurya154@\\gmail.com}
    \href{http://facebook.com/therajanmaurya}{fb://therajanmaurya}
  \section{languages}
    English \& Hindi
  \section{programming}
    {\color{red} $\varheartsuit$} Java(Android),Xml
    C And C++
    Python
    CSS3 \& HTML5
  \section{coursework}
    Calculus
    Linear Algebra
    Data Structures
    Algorithms
    Ordinary differential equations and
    complex analysis
    Discrete Mathematics
    Partial Differential Equations
    Data Modeling \& Design
    Operating System
    Computational Linguistics
    Analog Electronic
    Business, Entrepreneurship and
    Innovation Management
\end{aside}

\section{interests}

Android Development, Learning in computer algorithms , Android Animation, Web development , Making new GUI in Android with Material design.
 

\section{education}

\begin{entrylist}
  \entry
    {2015}
    {Graduation {\normalfont University of delhi}}
    {4th Sem | Delhi}
    {\emph{B.Tech In IT With Mathmatical Innovation}}
  \entry
    {2012} 
    {Intermediate}
    {RPVV Yamuna Vihar, Central Board of Secondary Education}
    {May 2012 | Delhi, India}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2014}
    {IT Maha-Abhiyaan}
    {Faridabad}
    {\emph{Summer Intern(June-Aug)}\\ Android developer, A Msme Tech. Development Program By Cluster innovation center \& Phd Chamber Of Commerce and Industry \& Iamsmeofindia. \newline Developed An Android App for the Iamsmeofindia that consist product and many other feature with Google Push Notification}

  \entry
    {2014}
    {PHD Chamber Of Commerce And Industry}
    {Delhi}
    {\emph{Summer Intern(Aug-Sept)}\\ Android developer, Developed an Android App for innovation submit of phd chamber. \begin{itemize}
    \item Collect the data of MSMEs including PHD chamber, NSIC, Niesbud, SIDBI etc.Categorize the data in five different sectors: Finance, Marketing, Trading,Schemes and News.
    \item Developed an android mobile application for MSMEs consist of the categorized data of MSMEs.
    \item Launched in Innovation Summit of PHD Chamber
    \end{itemize}}
  % \entry
  %   {06–08 2007}
  %   {LIP6/CNRS, Paris}
  %   {Research Internship.}
  %   {\emph{Kernels in real world networks.}}
   
\end{entrylist} 

\section{projects}

\begin{entrylist}
  \entry
    {2015}
    {\href{https://github.com/teamDAPSR/Trees-of-Delhi}{Tree Of Delhi}}
    {{Delhi}}
    {{Acadmic Project(Apr-Going On)} \\This is an Android App which will help us to identify Tree of Delhi on the basis of leafs.}

  \entry
    {2015}
    {\href{https://github.com/teamDAPSR/Antardhvani}{Antardhvani}}
    {{Delhi}}
    {{Official Android App of Cultral Festival Of University Of Delhi(Feb)} \\Official app for Antardhvani. This app is open source, source code can be found at above link\\
    Features :\\ • Location map using google map api. • App is upto latest Material design with parallax header. • Animated splash screen. and • Push notification}

  \entry
    {2015}
    {\href{https://github.com/therajanmaurya/Bulk-SMS-Service-final}{Bulk-SMS-Service}}
    {Delhi}
    {This Android application give the freedom to user to send single SMS to unlimited Person }
  \entry
    {2015}
    {\href{https://github.com/therajanmaurya/Flashing-Light}{Flashing-Light}}
    {Delhi}
    {This Android App is helping hand of disable people
    Feature:\\• Start Flashing Light whenever phone ringing. \\
    • Whenever phone ringing "saying caller name".\\
    • Manually Enable And Disable Flashing Light. }
\end{entrylist}
\end{document}